Untitled

### 2023-10-26 code/analysis_Redo.Rmd
Seeing changes in rival's complexity

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    tes <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 1:4){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "Sites", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "Total.Hours", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

df.rival <- dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
  bind_rows(dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(!is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
    select(`BHCMIS ID.x`, `BHCMIS ID`:Year, Att, ID) %>% 
    left_join(df.comp %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense, 
         fs_contributions = as.numeric(fs_contributions), 
         fs_program_service_revenue = as.numeric(fs_program_service_revenue), 
         fs_other = as.numeric(fs_other), 
         fs_miscellaneous = as.numeric(fs_miscellaneous), 
         ngla_sales_revenue = as.numeric(ngla_sales_revenue), 
         ngla_admin_expense = as.numeric(ngla_admin_expense), 
         fringe_rate = as.numeric(fringe_rate)) , by = c("BHCMIS ID.x" = "BHCMISID", "Year"))) %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100) %>% 
    select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total,MCD:COM, Pct.MCD, Pct.None, Pct.MCR, Pct.COM, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.Homeless, Assets, Staff)

>>>>

   model.dist.quants <-  did2s(
      data = df.spill3 %>% filter(Dist == 0) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1)), 
      yname = "Medicaid", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
    tes <- data.frame(model.dist.quants$coeftable)[1,]

  for (i in 1:4){
      model.dist.quants <-  did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i]))%>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "Medicaid", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    ) 
      tes <- rbind(tes, data.frame(model.dist.quants$coeftable)[1,])
  }

@@

did2s(
      data = df.spill3  %>% filter(Dist > quantile(Dist, qnats1[i]) & Dist <= quantile(Dist, qnats2[i])) %>% mutate(Hours = ifelse(Sites == 0, 0, Total.Hours / Sites), SL = log(Sites + 1))  , 
      yname = "NumberofPatients", 
      treatment = "Tx",
        first_stage = ~ 1 | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE)  ,
        cluster_var = "Zip",
      verbose = FALSE
    )

@@

df.rival <- dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
  bind_rows(dfc %>% 
    left_join(df.z.dist.plot %>% select(`BHCMIS ID.x`, `BHCMIS ID.y`), by = c("BHCMIS ID" = "BHCMIS ID.y")) %>% 
    filter(!is.na(`BHCMIS ID.x`)) %>% 
    unique() %>% 
    select(`BHCMIS ID.x`, `BHCMIS ID`:Year, Att, ID) %>% 
    left_join(df.comp %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense, 
         fs_contributions = as.numeric(fs_contributions), 
         fs_program_service_revenue = as.numeric(fs_program_service_revenue), 
         fs_other = as.numeric(fs_other), 
         fs_miscellaneous = as.numeric(fs_miscellaneous), 
         ngla_sales_revenue = as.numeric(ngla_sales_revenue), 
         ngla_admin_expense = as.numeric(ngla_admin_expense), 
         fringe_rate = as.numeric(fringe_rate)) , by = c("BHCMIS ID.x" = "BHCMISID", "Year"))) %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100) %>% 
    mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5) %>% 
    select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total,MCD:COM, Pct.MCD, Pct.None, Pct.MCR, Pct.COM, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.Homeless, Assets, Staff, Complexity, Intensity)
